Equalizer\\Programming and User Guide

### 2013-01-21 Developer/ProgrammingGuide/paper.tex
Merge cleanup

Written by Stefan Eilemann.\\
Contributions by Maxim Makhinya, Jonas B\"osch, Christian Marten, Sarah
Amsellem, Patrick Bouchaud, Philippe Robert, Robert Hauck and Lucas Peetz
Dulley.

@@

The \textsf{eq::Window} class encapsulates a drawable and an OpenGL
context. The drawable can be an on-screen window or an off-screen
pbuffer or framebuffer Object (FBO).

>>>>

Written by Stefan Eilemann.\\
Contributions by Daniel Nachbaur, Maxim Makhinya, Jonas B\"osch, Christian
Marten, Sarah Amsellem, Patrick Bouchaud, Philippe Robert, Robert Hauck and
Lucas Peetz Dulley.

@@

The \textsf{eq::Window} class encapsulates a drawable and an OpenGL
context. The drawable can be an on-screen window or an off-screen
pbuffer or framebuffer object (FBO).
